### 2021-05-10 papers/SYRCoSE/intro.tex
change repo address to current
why coq

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like \coq~\cite{Coq}, \agda~\cite{Agda}, 
\isabelle~\cite{Nipkow-al:Isabelle2002}, 
\arend~\cite{Arend}, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

@@

Our library together with the examples of 
its usage is available online at \url{https://github.com/volodeyka/event-struct}.

>>>>

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like \coq~\cite{Coq},
%\agda~\cite{Agda}, 
\isabelle~\cite{Nipkow-al:Isabelle2002}, 
\arend~\cite{Arend}, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

We have chosen \coq as the proof assistant because it's a mature formal proof management tool
with a rich ecosystem of libraries, plugins, documentation, and
existing applications including the certification of properties of programming languages:
the verified C compiler CompCert~\cite{Leroy-Compcert-CACM:2006},
the Verified Software Toolchain~\cite{Appel-ESOP2011} for verification of C programs,
and the Iris framework~\cite{Jung-al:JFP2018} for concurrent separation logic,
to name a few.

@@

Our library together with the examples of 
its usage is available online at \url{https://github.com/event-structures/event-struct}.
